Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-02-05 paper/paper.tex
updated randst arrow data and commented out triangle writing we had thus far in paper Tested everything on node32.

\section{Triangular Shapes}
\begin{figure}
  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-triangle}
\end{figure}

The double pole oscillation pattern, in which one pole is located in a
single corner of the triangle and the other pole is spread out between
the opposite two, can be seen in Figure \ref{box-triangle}.  The
equilateral triangle shows a spike in both the Center and Left
sections at the same time, both showing the familiar sequence of peaks
amoungst the different states of the protein seen in the poles of the
pill shaped bacteria.  A spike in the other corner, showing the common
sequence, occurs during the minima of the former two, wth a higher
concentration at the peak.  A similar pattern is seen in the
iscosolese triangular shape, where interestingly the onset of the
maxima in the single maxima corner (the Left section) builds more
quickly than it fades.  This is presumably becuase as the cytoplasmic
minD:ATP diffuses down a more accute corner, it is sourrounded by
closer cell walls than it would be in a less acute corner, so that the
it is more apt at any diffusive step to make contact and cluster on
the walls.  That particular part of the process is therefore
accelerated, driving the build up of the maxima forward.

The right triangle shows a similar pattern except that here there is
an assymetry between the two corners that maximize at roughly the same
time.  One corner is further from the single maximizing corner and it
consisitently peaks later.  The MinD simply have further to travel
before they maximize there.

For these three sizess and shapes there is not sign that the
oscillation patterns once they are set will break down.

\begin{figure}
%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
  \caption{Total protein fluctuation of an equilateral triangle with
    larger dimensions (each side is roughly $6\micron$.  The vertical
    axis shows stacked the total number of proteins that are of four
    different compound stages and in the different sections of the
    cell. The time limits have been set to show the broken down
    section of the simulation.}
  \label{box-triangle}

The larger equilateral shape shows the same pattern as the smaller
version does only until fifteen periods, at which point there is a
breakdown of the oscillation pattern.  During the last three stable
periods, the single maximizing corner, the lower left section in the
figure, has a lower peak each period as the membrane bound MinD:ATP in
the other corners lag more and more before being eaten away by the
MinE.  Finally these maxima lag so much that they break down the
regular pattern.  There then occurs about five periods of semi chaotic
behavoir, until it settles back into another stable oscillation that
is similar to the original one, except that a different corner has
been chosen to be the singlular maxima (the right section in the
figure), while the other two corners maximize at the same time.  This
interesting breakdown and recovery shows both the robustness of the
double pole oscilatory tendency and the importance of required
distance of travel for the different proteins.

\end{figure}

\subsubsection{Randst-99 our lambda shape}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}arrow-plot-NflD-randst-25-600-800-9800-1500.pdf

>>>>

\section{Triangular Shapes}

Still waiting for the triangle data to show what we expect.  We have
small triangles that gradually go from no oscillations to
oscillations, but the large triangle data does not yet show
irregularities.  I have very large simulations running that should
definitely show this at some point (Give it a few days).

%% \begin{figure}
%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
%%   \caption{Total protein fluctuation in the right, middle, and left
%%     parts of an equilateral (top), iscoscolese (middle), and 3-4-5
%%     (bottom) triangle.  The vertical axis shows stacked the total
%%     number of proteins that are of four different compound stages and
%%     in the different sections of the cell.}
%%   \label{box-triangle}
%% \end{figure}

%% The double pole oscillation pattern, in which one pole is located in a
%% single corner of the triangle and the other pole is spread out between
%% the opposite two, can be seen in Figure \ref{box-triangle}.  The
%% equilateral triangle shows a spike in both the Center and Left
%% sections at the same time, both showing the familiar sequence of peaks
%% amoungst the different states of the protein seen in the poles of the
%% pill shaped bacteria.  A spike in the other corner, showing the common
%% sequence, occurs during the minima of the former two, wth a higher
%% concentration at the peak.  A similar pattern is seen in the
%% iscosolese triangular shape, where interestingly the onset of the
%% maxima in the single maxima corner (the Left section) builds more
%% quickly than it fades.  This is presumably becuase as the cytoplasmic
%% minD:ATP diffuses down a more accute corner, it is sourrounded by
%% closer cell walls than it would be in a less acute corner, so that the
%% it is more apt at any diffusive step to make contact and cluster on
%% the walls.  That particular part of the process is therefore
%% accelerated, driving the build up of the maxima forward.

%% The right triangle shows a similar pattern except that here there is
%% an assymetry between the two corners that maximize at roughly the same
%% time.  One corner is further from the single maximizing corner and it
%% consisitently peaks later.  The MinD simply have further to travel
%% before they maximize there.

%% For these three sizess and shapes there is not sign that the
%% oscillation patterns once they are set will break down.

%% \begin{figure}
%% %%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
%%   \caption{Total protein fluctuation of an equilateral triangle with
%%     larger dimensions (each side is roughly $6\micron$.  The vertical
%%     axis shows stacked the total number of proteins that are of four
%%     different compound stages and in the different sections of the
%%     cell. The time limits have been set to show the broken down
%%     section of the simulation.}
%%   \label{box-triangle}
%% \end{figure}

%% The larger equilateral shape shows the same pattern as the smaller
%% version does only until fifteen periods, at which point there is a
%% breakdown of the oscillation pattern.  During the last three stable
%% periods, the single maximizing corner, the lower left section in the
%% figure, has a lower peak each period as the membrane bound MinD:ATP in
%% the other corners lag more and more before being eaten away by the
%% MinE.  Finally these maxima lag so much that they break down the
%% regular pattern.  There then occurs about five periods of semi chaotic
%% behavoir, until it settles back into another stable oscillation that
%% is similar to the original one, except that a different corner has
%% been chosen to be the singlular maxima (the right section in the
%% figure), while the other two corners maximize at the same time.  This
%% interesting breakdown and recovery shows both the robustness of the
%% double pole oscilatory tendency and the importance of required
%% distance of travel for the different proteins.

\section{Our 'V' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}arrow-plot-NflD-randst-25-600-800-9800-1500.pdf
